---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coRal

<!-- badges: start -->
<!-- badges: end -->

The goal of coRal is to ...

## Installation

You can install coRal from [GitHub](https://github.com/Allgeier-Lab/coRal) with the following line of code. You will need the `auth_token` because the repository is currently set to private so only members of the Allgeier Lab can see it. **PlEASE DON'T SHARE THIS TOKEN WITH ANYONE WITHOUT LETTING ME KNOW FIRST**.

``` {r install}
remotes::install_github("Allgeier-Lab/coRAL", 
                        auth_token = "e46c8683663fd7a14869c949a48582063e64b915")
```

<!-- Add CRAN link if applicable -->

## Example

To access all functions to run the mode, simply load the library. 

```{r example}
library(coRal)
```

The starting values and parameters must be imported as two separated list with a named object for each value. There is a function to import these values and automatically convert them to a list (`read_parameters`). The files must be a table with two columns. The first column must be called "parameter" and include a string of all parameter names. The second column must the called "value" and include the actual values.

To check if all parameters are available, use `check_parameters`.


```{r check_parameters}
starting_values <- system.file("extdata", "starting_values.csv", package = "coRal")
parameters <- system.file("extdata", "parameters.csv", package = "coRal")

starting_values <- read_parameters(file = starting_values, sep = ";")
parameters <- read_parameters(file = parameters, sep = ";")

check_parameters(starting_values = starting_values, parameters = parameters)
```

To setup the simulation seafloor and individuals, simply run `setup_seafloor` and `setup_population`. If you want to add artificial reefs to the seafloor, provide a `matrix` with x,y coordinates of all AR cells.

```{r setup}
reef_matrix <- matrix(data = c(-1, 0, 0, 1, 1, 0, 0, -1, 0, 0), 
                      ncol = 2, byrow = TRUE)

input_seafloor <- setup_seafloor(extent = c(50, 50), grain = 1, reefs = reef_matrix, 
                                       starting_values = starting_values, parameters = parameters)

input_fish_population <- setup_fish_population(seafloor = input_seafloor, 
                                               starting_values = starting_values, 
                                               parameters = parameters)
```

To rum a simulation, simply provide the previously created seafloor and population as well as all parameters and starting values the `run_simulation` function. Additionally, you need to specify the number of time steps that are simulated.

```{r run_sim}
result <- run_simulation(seafloor = input_seafloor, 
                         fish_population = input_fish_population, 
                         starting_values = starting_values, parameters = parameters, 
                         reef_attraction = TRUE,
                         max_i = 50, verbose = FALSE)
```

The animate the results, pass the resulting object to `animate_result`. This will produce a GIF, but you need the packages `ggplot2`, `gganimate` and `gifski`.

```{r animate_sim, fig.align="center"}

animate_result(result, fill = "detritus_pool", end_pause = 10)

``` 

### Code of Conduct

Please note that the coRal project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
