---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coRal

<!-- badges: start -->
<!-- badges: end -->

The goal of coRal is to ...

## Installation

You can install coRal from [GitHub](https://github.com/Allgeier-Lab/coRal) with:

``` r
remotes::install_github("Allgeier-Lab/coRAL")
```

<!-- Add CRAN link if applicable -->

## Example

To access all functions to run the mode, simply load the library. 

```{r example}
library(coRal)
```

The starting values and parameters must be imported as two separated list with a named object for each value. There is a function to import these values and automatically convert them to a list (`read_parameters`). The files must be a table with two columns. The first column must be called "parameter" and include a string of all parameter names. The second column must the called "value" and include the actual values.

To check if all parameters are available, use `check_parameters`.


```{r check_parameters}
starting_values <- system.file("extdata", "starting_values.csv", package = "coRal")
parameters <- system.file("extdata", "parameters.csv", package = "coRal")

starting_values <- read_parameters(file = starting_values, sep = ";")
parameters <- read_parameters(file = parameters, sep = ";")

check_parameters(starting_values = starting_values, parameters = parameters)
```

To setup the simulation environment and individuals, simply run `setup_environment` and `setup_population`. If you want to add artifical reefs to the environment, provide a `matrix` with x,y coordinates of all AR cells.

```{r setup}
reef_matrix <- matrix(data = c(-1, 0, 0, 1, 1, 0, 0, -1, 0, 0), 
                      ncol = 2, byrow = TRUE)

input_environment <- setup_environment(extent = c(100, 100), grain = 1, reefs = reef_matrix, 
                                       starting_values = starting_values, parameters = parameters)

input_population <- setup_population(environment = input_environment, 
                                     starting_values = starting_values, parameters = parameters)
```

### Code of Conduct

Please note that the coRal project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
