---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Please see `vignette("general-background")` for a general model description of **arrR**. To get a BibTex entry, please use `citation("arrR")` or see `vignette("publication-record")`.

## How to use **arrR**

```{r setup, message = FALSE, warning = FALSE}
library(arrR)
library(dplyr)
library(ggplot2)
```

You can always use `?` in front of a function to see the help page. For many functions, there are additionally arguments which you can specify, which are not necessarily explained here.

### 1. Import and change starting values and parameters

After you installed and loaded the package, you can access default/exemplary starting values and parameters of the model. Since both objects are just named lists, you can easily change certain parameters. If you pass the objects to `check_parameters()`, the function will check if all required values are available and return warnings if not. 

Of course, you can also load your own data as a list containing starting values and parameters. The `read_parameters()` function can help with this. You can also create the starting values and parameter lists completely from scratch as long as they are two named lists containing all required values.

Please see `vignette("starting-values-parameters")` for more information about all parameters.

```{r check_parameters}
# get starting values
starting_values <- arrR::arrR_starting_values

# get parameters
parameters <- arrR::arrR_parameters

# change some starting values and parameters
starting_values$pop_n <- 8

parameters$pop_reserves_max <- 0.1

parameters$seagrass_thres <- -1/4

# check if all parameters are present and meaningful
check_parameters(starting_values = starting_values, parameters = parameters)
```

### 2. Setup seafloor and fish population

Next, you need to setup the seafloor and the fish population. If you want to add artificial reefs (ARs), simply provide a `matrix` with *x*- and *y*-coordinates of all reef cells. The center cell always has the coordinate *x,y(0,0)*. Additionally, when setting up the seafloor, you need to specify the dimensions in *x*- and *y*-directions and the grain of one cell.

The function `get_stable_values` allows to calculate the nutrients and detritus amount to keep the whole ecosystem theoretical stable (excluding fish detritus consumption and nutrient excretion). The values can be used to set up the simulation environment.

```{r setup_inputs}
# create 5 reef cells in center of seafloor
reef_matrix <- matrix(data = c(-1, 0, 0, 1, 1, 0, 0, -1, 0, 0), 
                      ncol = 2, byrow = TRUE)

# get stable nutrient/detritus values
stable_values <- get_stable_values(bg_biomass = starting_values$bg_biomass,
                                   ag_biomass = starting_values$ag_biomass,
                                   parameters = parameters)

starting_values$nutrients_pool <- stable_values$nutrients_pool

starting_values$detritus_pool <- stable_values$detritus_pool

# create seafloor
input_seafloor <- setup_seafloor(dimensions = c(100, 100), grain = 1, 
                                 reef = reef_matrix, starting_values = starting_values)

# create fishpop
input_fishpop <- setup_fishpop(seafloor = input_seafloor, 
                               starting_values = starting_values, 
                               parameters = parameters)
```

### 3. Run the model

The `run_simulation()` function is the core function of the package that starts a simulation run. You only need to provide the previously created seafloor and fish population as well as the parameters. Additionally, you need to specify the total run time of the simulation (in # of iterations called *i* here).

Further, you can specify how often all seagrass related processes should be simulated, e.g. only once a day using `seagrass_each`. 

Last, because the produced output can be quite large, you can save only every *j* iterations, specified by `save_each`. The model will still simulate all processes each iteration, however, only safe and return the specified iterations to reduce the required memory.

One of the most important function arguments of `run_simulation()` is the `movement` argument, which specifites how individiauls move across the simulation environment. For more information, please see `vignette("movement-behaviors")`.

```{r run_sim}
# one iterations equals 120 minutes
min_per_i <- 120

# run the model for ten years
years <- 10
max_i <- (60 * 24 * 365 * years) / min_per_i

# run seagrass once each day
days <- 1
seagrass_each <- (24 / (min_per_i / 60)) * days

# save results only every 365 days
days <- 365
save_each <- (24 / (min_per_i / 60)) * days

result <- run_simulation(seafloor = input_seafloor, fishpop = input_fishpop,
                         parameters = parameters, movement = "attr",
                         max_i = max_i, min_per_i = min_per_i, 
                         seagrass_each = seagrass_each, save_each = save_each)
```

### 4. Look at model results

You can get a first glance and the results simply printing the model output. This gives you some summary statistics at the last iteration of the model.

```{r print_result}
# print model results
result
```

The returning object `mdl_rn` object is simply a list "under the hood", so analyzing the results yourself should be pretty straightforward. Simply access the data you need. 

```{r access_result, fig.align = "center"}
# show all elements of result list
names(result)

# show e.g. result for fish population
head(result$fishpop)

# get results of fish population of the final timestep and plot weight ~ length
(final_fishpop <- dplyr::filter(result$fishpop, timestep == max(timestep)) %>% 
  ggplot2::ggplot(ggplot2::aes(x = length, y = weight)) + 
    ggplot2::geom_point(shape = 1) + 
    ggplot2::geom_smooth(method = "lm", formula =  "y ~ x", size = 0.5) +
    ggplot2::labs(x = "Length [cm]", y = "Weight [g]") +
    ggplot2::theme_classic())

```

Lastly, you can plot the results. Make sure to also check out the `summarize` argument of the plot function. 

```{r plot_result, fig.align = "center"}
# plot map of seafloor
plot(result, what = "seafloor")
```

### 5. Various

**arrR** comes with many helper functions, such as `get_density()`, `get_limits()`, `filter_mdlrn()` or `summarize_mdlrn()`. Make sure to check out the [Index](https://allgeier-lab.github.io/arrR/reference/index.html) for an overview.
