---
title: "2. Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{2. Get started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Please see the [General background](general-background.html) vignette for a general overview of *arrR*. To get a BibTex entry, please use `citation("arrR")`.

## How to use `arrR`

```{r setup, message = FALSE, warning = FALSE}
library(arrR)
library(dplyr)
library(ggplot2)
```

You can always use `?` in front of a function to see the help page. For many functions, there are additionally options you can specify which are not necessarily explained here.

### 1. Import and change starting values and parameters

After you installed and loaded the package, you can access default/exemplary starting values and parameters of the model. Since both objects are simply named lists, you can easily change certain parameters. If you pass the objects to `check_parameters`, the function will check if all required values are available.

Please see the [Starting values and parameters](starting-values-parameters.html) vignette for more information about all parameters.

```{r check_parameters}
# get starting values
starting_values <- arrR::arrR_starting_values

# get paramters
parameters <- arrR::arrR_parameters

# change some starting values and parameters
starting_values$pop_n <- 8

parameters$pop_reserves_max <- 0.1

# check if all parameters are present and meaningful (to a degree...)
check_parameters(starting_values = starting_values, parameters = parameters)
```

Of course, you can import or create the starting values and parameter list completely from scratch as long as they are two named lists containing all required values.

### 2. Setup seafloor and fish population

Next, you need to setup the seafloor and the fish population. If you want to add artificial reefs, simply provide a `matrix` with *x*- and*y*-coordinates of all reef cells. The center cell always has the coordinate (0,0).

```{r setup_inputs}
# create 5 reef cells in center of seafloor
reef_matrix <- matrix(data = c(-1, 0, 0, 1, 1, 0, 0, -1, 0, 0), 
                      ncol = 2, byrow = TRUE)

# create seafloor
input_seafloor <- setup_seafloor(dimensions = c(100, 100), grain = 1, 
                                 reefs = reef_matrix, 
                                 starting_values = starting_values)

# create fishpop
input_fishpop <- setup_fishpop(seafloor = input_seafloor, 
                               starting_values = starting_values, 
                               parameters = parameters)
```

### 3. Run the model

The `run_simulation` functions starts a simulation run. You only need to provide the previously created seafloor and fish population as well as the parameters. Additionally, you need to specify the total run time of the simulation (in # of iterations, called timesteps here).

```{r run_sim, echo = FALSE}
result <- arrR:::result_readme
```

```{r run_sim_dummy, eval = FALSE}
min_per_i <- 120

# run the model for ten years
years <- 10
max_i <- (60 * 24 * 365 * years) / min_per_i

# save results only every 365 days
days <- 365
save_each <- (24 / (min_per_i / 60)) * days

# run seagrass once each day
days <- 1
seagrass_each <- (24 / (min_per_i / 60)) * days

result <- run_simulation(seafloor = input_seafloor, fishpop = input_fishpop,
                         parameters = parameters, movement = "rand",
                         max_i = max_i, min_per_i = min_per_i, 
                         seagrass_each = seagrass_each, save_each = save_each)
```

### 4. Look at model results

You can get a first glance and the results simply printing the model output. This gives you some summary statistics at the last timesteps of the model.

```{r print_result}
# print model results
result
```

The returning object is simply a list, so analyzing the results yourself should be pretty straightforward. Simply access the data you need. 

```{r access_result, fig.align = "center"}
# show all elements of result list
names(result)

# show e.g. result for fish population
head(result$fishpop)

# get results of fish population of the final timestep and plot weight ~ length
(final_fishpop <- dplyr::filter(result$fishpop, timestep == max(timestep)) %>% 
  ggplot2::ggplot(ggplot2::aes(x = length, y = weight)) + 
    ggplot2::geom_point(shape = 1) + 
    ggplot2::geom_smooth(method = "lm", formula =  "y ~ x", size = 0.5) +
    ggplot2::labs(x = "Length [cm]", y = "Weight [g]") +
    ggplot2::theme_classic())

```

Lastly, you can plot the results. Make also sure to check out the `summarize` argument of the plot function. 

```{r plot_result, fig.align = "center"}
# plot map of seafloor
plot(result, what = "seafloor")
```

