---
title: "3. Starting values and parameters"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{3. Starting values and parameters}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
```

Please see the [Get started](getstarted.html) vignette for a quick tutorial how to use `arrR`.

To see a full list all needed starting values and parameters, simply run `check_parameters()`. Both starting values and parameters must be provided as named lists. The package contains a set of default values you can easily access (`default_parameters`, `default_starting_values`).

## Starting values

```{r, sarting_values, echo = FALSE}
starting_values_df <- data.frame(name = c("ag_biomass", 
                                          "bg_biomass", 
                                          
                                          "nutrients_pool", 
                                          "detritus_pool", 
                                          
                                          "pop_n", 
                                          "pop_mean_size", 
                                          "pop_var_size"), 
                                 
                                 fun = c("setup_seafloor()", 
                                         "setup_seafloor()", 
                                         
                                         "setup_seafloor()",
                                         "detritus_pool()", 
                                         
                                         "setup_fishpop()", 
                                         "setup_fishpop()", 
                                         "setup_fishpop()"), 
                                 
                                 descr = c("Starting aboveground biomass", 
                                           "Starting belowground biomass", 
                                           
                                           "Starting nutrients pool", 
                                           "Starting detritus biomass", 
                                           
                                           "Number of fish individuals", 
                                           "Mean fish individual size", 
                                           "Variation fish individual size"))
                
knitr::kable(starting_values_df, col.names = c("Name", "Function", "Describtion"), align = "lrr") %>% 
  kableExtra::kable_styling(full_width = TRUE, position = "center", font_size = 12, )
```

## Parameters

```{r, parameters, echo = FALSE}
parameter_df <- data.frame(
  name = c("ag_biomass_max", 
           "ag_biomass_min", 
           "ag_v_max", 
           "ag_k_m",
           "ag_gamma",
                                    
           "bg_biomass_max", 
           "bg_biomass_min", 
           "bg_v_max", 
           "bg_k_m", 
           "bg_gamma", 
           
           "seagrass_thres",
           "seagrass_slope",
           "seagrass_slough",
                                    
           "nutrients_diffusion", 
           "nutrients_output", 
           
           "detritus_mineralization",
           "detritus_diffusion",
           "detritus_fish_decomp",
           "detritus_fish_diffusion",
           
           "move_mean",
           "move_var",
           "move_visibility",
           "move_border",
           "move_reef",
           "move_return",
       
           "pop_max_reserves",
           "pop_thres_reserves_min",
           "pop_thres_reserves_max",
           "pop_consumption_prop",

           "pop_a",
           "pop_b",
           "pop_k",
           "pop_linf",
           "pop_n_body",
           
           "resp_intercept", 
           "resp_slope", 
           "resp_temp_low", 
           "resp_temp_optm", 
           "resp_temp_max"), 
  
  fun = c("rcpp_seagrass_growth()", 
          "rcpp_seagrass_growth()", 
          "rcpp_seagrass_growth()", 
          "rcpp_seagrass_growth()",
          "rcpp_seagrass_growth()", 
          
          "rcpp_seagrass_growth()", 
          "rcpp_seagrass_growth()", 
          "rcpp_seagrass_growth()", 
          "rcpp_seagrass_growth()",
          "rcpp_seagrass_growth()",
          
          "rcpp_seagrass_growth()", 
          "rcpp_seagrass_growth()",
          "rcpp_seagrass_growth()",
          
          "rcpp_mineralization()",
          "rcpp_mineralization()",
          
          "rcpp_mineralization()",
          "rcpp_mineralization()",
          "rcpp_mineralization()",
          "rcpp_mineralization()",
          
          "simulate_movement()",
          "simulate_movement()",
          "simulate_movement()",
          "simulate_movement()",
          "simulate_movement()",
          "simulate_movement()",
          
          # update functions
          "pop_max_reserves",
          "pop_thres_reserves_min",
          "pop_thres_reserves_max",
          "pop_consumption_prop",
          
          "pop_a",
          "pop_b",
          "pop_k",
          "pop_linf",
          "pop_n_body",
    
          "rcpp_respiration()", 
          "rcpp_respiration()", 
          "rcpp_respiration()", 
          "rcpp_respiration()", 
          "rcpp_respiration()"),
  
  # update description
  descr = c("Maximum value of aboveground biomass", 
            "Minimum value of aboveground biomass", 
            "ag_v_max", 
            "ag_k_m",
            "ag_gamma",
                                     
            "bg_biomass_max", 
            "bg_biomass_min", 
            "bg_v_max", 
            "bg_k_m", 
            "bg_gamma", 
            
            "seagrass_thres",
            "seagrass_slope",
            "seagrass_slough",
                                     
            "nutrients_diffusion", 
            "nutrients_output", 
            
            "detritus_mineralization",
            "detritus_diffusion",
            "detritus_fish_decomp",
            "detritus_fish_diffusion",
            
            "move_mean",
            "move_var",
            "move_visibility",
            "move_border",
            "move_reef",
            "move_return",
        
            "pop_max_reserves",
            "pop_thres_reserves_min",
            "pop_thres_reserves_max",
            "pop_consumption_prop",
 
            "pop_a",
            "pop_b",
            "pop_k",
            "pop_linf",
            "pop_n_body",
           
            "resp_intercept", 
            "resp_slope", 
            "resp_temp_low", 
            "resp_temp_optm", 
            "resp_temp_max"))
                
knitr::kable(parameter_df, col.names = c("Name", "Function", "Describtion"), align = "lrr") %>% 
  kableExtra::kable_styling(full_width = TRUE, position = "center", font_size = 12, )
```

