---
title: "3. Starting values and parameters"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{3. Starting values and parameters}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
```

Please see the [Get started](getstarted.html) vignette for a quick tutorial how to use `arrR`.

To see a full list all needed starting values and parameters, simply run `check_parameters()`. Both starting values and parameters must be provided as named lists. The package contains a set of default values you can easily access (`default_parameters`, `default_starting_values`).

## Starting values

```{r, sarting_values, echo = FALSE}
starting_values_df <- data.frame(name = c("ag_biomass", 
                                          "bg_biomass", 
                                          "nutrients_pool", 
                                          "detritus_pool", 
                                          "pop_n", 
                                          "pop_mean_size", 
                                          "pop_var_size", 
                                          "water_temp"), 
                                 fun = c("setup_seafloor()", 
                                         "setup_seafloor()", 
                                         "setup_seafloor()",
                                         "detritus_pool()", 
                                         "setup_fishpop()", 
                                         "setup_fishpop()", 
                                         "setup_fishpop()", 
                                         "Not used"), 
                                 descr = c("Starting aboveground biomass", 
                                           "Starting belowground biomass", 
                                           "Starting nutrients pool", 
                                           "Starting detritus biomass", 
                                           "Number of fish individuals", 
                                           "Mean fish individual size", 
                                           "Variation fish individual size", 
                                           "Water temperature"))
                
knitr::kable(starting_values_df, col.names = c("Name", "Function", "Describtion"), align = "lrr") %>% 
  kableExtra::kable_styling(full_width = TRUE, position = "center", font_size = 12, )
```

## Parameters

```{r, parameters, echo = FALSE}
parameter_df <- data.frame(name = c("ag_biomass_max", 
                                    "ag_biomass_min", 
                                    "ag_v_max", 
                                    "ag_k_m", 
                                    "bg_biomass_max", 
                                    "bg_biomass_min", 
                                    "bg_v_max", 
                                    "bg_k_m", 
                                    "bg_thres", 
                                    "nutrients_diffusion", 
                                    "detritus_ratio", 
                                    "detritus_mineralization", 
                                    "detritus_diffusion",
                                    "detritus_fish_diffusion",
                                    "detritus_fish_ratio", 
                                    "pop_max_reserves", 
                                    "pop_want_reserves", 
                                    "pop_visibility",
                                    "pop_mean_move", 
                                    "pop_var_move", 
                                    "pop_a", 
                                    "pop_b", 
                                    "pop_k",
                                    "pop_linf", 
                                    "pop_n_body", 
                                    "resp_intercept", 
                                    "resp_slope", 
                                    "resp_temp_low", 
                                    "resp_temp_optm", 
                                    "resp_temp_max"), 
                                 fun = c("simulate_seagrass()", 
                                         "simulate_seagrass()", 
                                         "simulate_seagrass()", 
                                         "simulate_seagrass()",
                                         "simulate_seagrass()", 
                                         "simulate_seagrass()", 
                                         "simulate_seagrass()", 
                                         "simulate_seagrass()", 
                                         "simulate_seagrass()", 
                                         "simulate_diffusion()",
                                         "simulate_seagrass()", 
                                         "simulate_mineralization()", 
                                         "simulate_diffusion()",
                                         "simulate_diffusion()",
                                         "simulate_mineralization()", 
                                         "setup_fishpop() simulate_fishpop_growth()", 
                                         "setup_fishpop() simulate_fishpop_growth(); simulate_mortality()", 
                                         "simulate_movement()", 
                                         "simulate_movement()", 
                                         "simulate_movement()", 
                                         "setup_fishpop() simulate_fishpop_growth()", 
                                         "setup_fishpop() simulate_fishpop_growth()", 
                                         "setup_fishpop() simulate_fishpop_growth()", 
                                         "setup_fishpop() simulate_fishpop_growth() simulate_mortality()", 
                                         "setup_fishpop() simulate_fishpop_growth() simulate_mortality()", 
                                         "simulate_respiration()", 
                                         "simulate_respiration()",
                                         "simulate_respiration()",
                                         "simulate_respiration()",
                                         "simulate_respiration()"), 
                                 descr = c("Maximum aboveground biomass", 
                                           "Minimum aboveground biomass",
                                           "Maximum nutrient uptake rate (aboveground)", 
                                           "Half-saturation nutrient uptake (aboveground)",
                                           "Maximum belowground biomass", 
                                           "Minimum belowground biomass",
                                           "Maximum nutrient uptake rate (belowground)", 
                                           "Half-saturation nutrient uptake (belowground)", 
                                           "Threshold of belowground biomass at aboveground biomass starts to grow",
                                           "Share of nutrients pool that is diffused to neighboring grid cell", 
                                           "Share of aboveground/belowground biomass that is sloughed to detritus biomass",
                                           "Share of detritus biomass that is mineralized to nutrients pool", 
                                           "Share of detritus biomass that is diffused to neighboring grid cell", 
                                           "Share of fish detritus biomass that is diffused to neighboring grid cell", 
                                           "Share of fish detritus biomass thas is mineralized to detritus biomass", 
                                           "Maximum amount of reserves in relation to body size", 
                                           "Starting reserves in relation to body size", 
                                           "Distance at which individuals have information about distance to reef", 
                                           "Mean movement distance", 
                                           "Variation movement distance", 
                                           "Length-Weight conversion", 
                                           "Length-Weight conversion", 
                                           "Bertalanffy growth curve", 
                                           "Bertalanffy growth curve", 
                                           "Share of nutrients in relation to body size", 
                                           "Intercept of allometric mass function", 
                                           "Slope of allometric mass function", 
                                           "Rate at which resp increases over low water temp", 
                                           "Optimum water temperature", 
                                           "Maximum water temperature"))
                
knitr::kable(parameter_df, col.names = c("Name", "Function", "Describtion"), align = "lrr") %>% 
  kableExtra::kable_styling(full_width = TRUE, position = "center", font_size = 12, )
```

