---
title: "Movement behaviors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Movement behaviors}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(arrR)
```

## Movement behaviors

The **arrR** model allows to specify different movement behaviors for each model run.

Fish movement is simulated using a movement distance and direction. How these distance and directions are simulated for each individual depends on the type of movement.

If an individual moves outside the seafloor environment, it re-enters it on the opposite side ("torus translation"). 

### Random movement

A random distance is sampled from a log-normal distribution using `move_mean` and `move_var` as mean and variance, respectively. A random directions is sampled from uniform distribution (0° <= direction <= 360°).

### Attracted movement

A random distance is sampled from a log-normal distribution using `move_mean` and `move_var` as mean and variance, respectively. In contrast to random movement, fish individuals perceive the relative distance to the artificial reef cells in three fixed directions ahead of them (45° left, 0° straight and 45° right) and always move in the direction that is the shortest to an artificial reef cell.

### Behavioral movement

_...Work in progress..._

1) Individuals move randomly (see "Random movement" above) and forage until their energy reserves are filled completely. 

2) If energy reserves are filled completely, individuals move directly towards the reef using either a random distance sampled from a log-normal distribution using `move_return` or the distance to the closest reef cell (if this distance is shorter than `move_return`) as mean. The direction is the direct bearing towards the reef cell. During this behavior, individuals do not forage.

3) Individuals are considered to be "on the reef" if their distance to the closest reef cell is less than `move_border`. Individuals move randomly using a distance sampled from a log-normal distribution using `move_reef` as mean until their energy reserves are below `pop_reserves_thres`. During this behavior, individuals do not forage.
